---
title       : Developing data products
subtitle    : Predicting child height
author      : Daniel Zuluaga
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Overview

This data product used dataset GaltonFamilies, in the [HistData](https://cran.r-project.org/web/packages/HistData/) R package, to predicts height of child through his gender and the height of the parents.

Presentation is being created as part of the peer assessment for the Coursera Developing Data Products. The assignment is geared toward ensuring the following concepts were well understood by the students:

* Shiny to build data product application
* Slidify to create data product related presentations

--- .class #id 

## Data loading and preprocessing

```{r, eval=FALSE}
library(HistData)
library(dplyr)
library(GGally)
library(ggplot2)

# loading dataset
gf <- data("GaltonFamilies")

# transform inches to cms
gf <- gf %>% mutate(fh=father*2.54,
                    mh=mother*2.54,
                    mph=midparentHeight*2.54,
                    ch=childHeight*2.54)

# fit different linear models for testing
m1 <- lm(ch ~ mph, data=gf)
m2 <- lm(ch ~ mph + gender, data=gf)
m3 <- lm(ch ~ fh + mh + gender, data=gf)
```


--- .class #id 

## asd

```{r, echo=FALSE, warning=FALSE}
library(HistData)
library(GGally)
library(ggplot2)

data(GaltonFamilies)
df <- GaltonFamilies[,c("childHeight", "father", "mother", "midparentHeight", "gender")]
ggpairs(df, lower=list(combo=wrap("facethist", binwidth=0.8)))
```


